\begin{thebibliography}{99}

	
	\bibitem{apptio}
	Apptio. Kubernetes Cost Optimization: A FinOps Guide.
	
	\bibitem{hamzeh2020}
	Hamzeh, H. (2020). A Multi-Resource Fair Scheduling Algorithm in Cloud Computing. PhD Thesis. Bournemouth University.
	
	\bibitem{imdoukh2019}
	Imdoukh, M., Ahmad, I., \& Al-Failakawi, M. G. (2019). Proactive autoscaling for web applications using Prophet and LSTM. Frontiers in Computer Science.
	
	\bibitem{khan2024}
	Khan, A. Q. (2024). Cloud Cost Modelling and Optimisation: A Taxonomy and Approaches for Storage Object Classification and Cloud Resource Placement. PhD Thesis. Norwegian University of Science and Technology (NTNU).
	
	\bibitem{k8sdocs}
	Kubernetes Authors. Official Kubernetes Documentation.
	
	\bibitem{mohamed2021}
	Mohamed, A., \& Sakr, S. (2021). Statistical Techniques for Characterizing Cloud Workloads: A Survey. International Journal of Cloud Applications and Computing (IJCAC).
	
	\bibitem{poseidon2019}
	Poseidon-Firmament Scheduler: Flow Network Graph-Based Scheduler for Kubernetes. Kubernetes Blog. (2019).
	
	\bibitem{rahman2025}
	Rahman, M. M., \& Al Dmour, I. (2025). A Hybrid Model-Based Proactive Autoscaling Architecture for Kubernetes Using Facebook Prophet and Long Short-Term Memory. Frontiers in Computer Science.
	
	\bibitem{stormforge}
	StormForge. Machine Learning for Kubernetes Resource Management. CloudBolt Blog.
	
	\bibitem{moonlight}
	The Moonlight. Cloud Resource Allocation with Convex Optimization.
	
	\bibitem{wang2023}
	Wang, Y.-C., et al. (2023). Delay-Aware Container Scheduling in Kubernetes. IEEE Internet of Things Journal.
	
	\bibitem{wiz}
	Wiz. AI/ML on Kubernetes: Best Practices for Resource Management, Security, and Observability.
	
	\bibitem{yakubov2025}
	Yakubov, D., \& Hästbacka, D. (2025). Empirical Analysis of Lightweight Kubernetes Distributions for Edge Computing. arXiv preprint.
	
	\bibitem{zhang2025}
	Zhang, Q., et al. (2025). Distributedness based scheduling. arXiv preprint.
	
	\bibitem{debbi2021}
	Debbi, H. (2021). Modeling and Performance Analysis of Resource Provisioning in Cloud Computing using Probabilistic Model Checking. Informatica, 45, 529–541.
	
	\bibitem{sedai}
	Sedai. Bin Packing and Cost Savings in Kubernetes Clusters on AWS.
	
	\bibitem{spot}
	Spot by NetApp. Kubernetes Cost Optimization: Challenges and Best Practices.
	
	\bibitem{zou2025}
	Zou, J., et al. (2025). Optimizing Web Application Placement in Kubernetes with a Machine Learning Custom Scheduler. Applied Sciences.
	
	\bibitem{reddy2020}
	Reddy, G. R., et al. (2020). Cloud resource optimization based on poisson linear deep gradient learning for mobile cloud computing. Journal of Intelligent \& Fuzzy Systems.
	
	\bibitem{ghaffari2015}
	Ghaffari, M. (2015). Near-Optimal Distributed Maximum Flow. Proceedings of the ACM Symposium on Principles of Distributed Computing (PODC).
	
	\bibitem{tarjan1984}
	Tarjan, R. E., \& Yannakakis, M. (1984). Scheduling Graphs on Two Processors. SIAM Journal on Computing.
	
	\bibitem{liu2017}
	Liu, Y., \& Wu, M. (2017). Real-time scheduling techniques for distributed systems. Journal of Systems Architecture.
	
	\bibitem{chen2020}
	Chen, Y., et al. (2020). Load balancing techniques in distributed and cloud computing. ACM Computing Surveys.
	
	\bibitem{kumar2019}
	Kumar, A. (2019). A Survey on Task Graph Scheduling Heuristic Algorithms in Distributed Computing System. International Journal of Engineering and Advanced Technology (IJEAT).
	
	\bibitem{shahidinejad2023}
	Shahidinejad, A., et al. (2023). Characterizing Web Application Workloads: A Systematic Literature Review and Clustering-Based Analysis. arXiv preprint.
	
	\bibitem{pogonip}
	Pogonip: A Scheduler for Asynchronous Microservices in Edge Computing Environments.
	
	\bibitem{k8sresources}
	Kubernetes Authors. Managing Resources for Containers.
	
\end{thebibliography}